A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-09-27 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added steady state behavior figure
explained steady state behavior

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Results}
\subsection{Emergence of steady state behavior}
Using the single run experiment, we discover that steady state behavior
begins at around 400 blocks. This appears due to the smoothening out of bootstrapping
effects. (NEED TO CHECK SIM AS STEADY STATE SEEMS TO BE IN FLUX)

\begin{figure}
    \includegraphics[width=\linewidth]{steady_state.png}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{Simulation_paper.bib}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multicol}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\section{Results}
\subsection{Emergence of steady state behavior}
Using the single run experiment, we discover that system stabalizes to steady state
usually around 400 blocks, usually due to normalization of bootstrapping states. 
However, final steady state values for the percentage of total groups that are compromised
appears to vary significantly and is dependent on the degree of concentration in the 
stake distribution.

For concentrated distributions such as Ethereum, the steady state level of compromised
groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
distribution, we see steady steat levels within the 60-80 percent band for the given set
of parameters (NOTE PARAMETER SETTINGS). \ref{fig:steady_state}

@@

\newpage

\begin{figure*}[h]
    \onecolumn
    \centering
    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
\end{figure*}

\newpage
\bibliographystyle{plain}
\bibliography{Simulation_paper.bib}
\end{document}
